Analysis for Biracial Grade Retention Project

### 2021-11-24 analysis/analysis.Rmd
Fix double caption

knitreg(map(results_monoracial, convert_marg),
        caption="Differences in the probability of being behind grade by race based on various statistical models. All estimates are average marginal effects.",
        digits=3, caption="Average marginal differences in probability of being behind grade relative to whites",
        custom.gof.rows=list("State fixed effects" =  c("No","Yes","Yes","Yes","Yes"),
                             "Year fixed effects" =   c("No","Yes","Yes","Yes","Yes"),
                             "Grade fixed effects" =  c("No","Yes","Yes","Yes","Yes"),
                             "Metro fixed effects" =  c("No","Yes","Yes","Yes","Yes"),
                             "Nativity and language" = c("No","No","Yes","Yes","Yes"),
                             "Parent's education" =    c("No","No","No","Yes","Yes"),
                             "Family resources" =      c("No","No","No","No","Yes")))
```

>>>>

knitreg(map(results_monoracial, convert_marg),
        digits=3, caption="Average marginal differences in probability of being behind grade relative to whites",
        custom.gof.rows=list("State fixed effects" =  c("No","Yes","Yes","Yes","Yes"),
                             "Year fixed effects" =   c("No","Yes","Yes","Yes","Yes"),
                             "Grade fixed effects" =  c("No","Yes","Yes","Yes","Yes"),
                             "Metro fixed effects" =  c("No","Yes","Yes","Yes","Yes"),
                             "Nativity and language" = c("No","No","Yes","Yes","Yes"),
                             "Parent's education" =    c("No","No","No","Yes","Yes"),
                             "Family resources" =      c("No","No","No","No","Yes")))
```
